### 2014-09-26 text/Chapter04.tex
Cleanup files, fix some invalid references
Add proof for bottom pointed substitution (Appendix A)

Furthermore, the $\cunit$ coeffect is often the top (greatest) or the bottom (smallest) 
element of the semi-lattice, but not in general. When this is the case, we are able
to prove certain properties of the calculus (Section~\ref{sec:syntax}).

@@

The call-by-value evaluation strategy holds for a wide range of flat coeffect calculi, including all
our three examples. However, it is rather weak -- in order to use it, the concrete semantics needs
to provide a way for reducing context-dependent term $\coctx{\Gamma}{\cclrd{r}} \vdash e : \tau$ to
a term $\coctx{\Gamma}{\cunit} e' : \tau$ with no context requirements.

@@

\begin{lemma}[Bottom-pointed substitution]
\label{thm:cbn-substitution-bot}
In a bottom-pointed flat coeffect calculus with an algebra $(\C, \cseq, \cpar, \czip, \cunit, \czero, \cleq)$ 
where $\czip = \cseq = \cpar$ and the operation is also idempotent and commutative:
%
\begin{equation*}
\begin{array}{l}
\coctx{\Gamma}{\cclrd{s}} \vdash e_s : \tau_s \;\; \wedge \;\; 
\coctx{\Gamma_1,  x : \tau_s, \Gamma_2}{ \cclrd{r}  } \vdash e_r : \tau_r\\
\quad \Rightarrow \;\; \coctx{\Gamma_1,\Gamma,\Gamma_2}{ \cclrd{r} \,\cseq\, \cclrd{s} } \vdash \subst{e_r}{x}{e_s} : \tau_r
\end{array}
\end{equation*}

\end{lemma}
\begin{proof}
By induction over $\vdash$, using the idempotent, commutative monoid structure to keep $\cclrd{s}$ with
the free-variable context. See Appendix~?.
\end{proof}

>>>>

Furthermore, the $\cunit$ coeffect is often the top (greatest) or the bottom (smallest) 
element of the semi-lattice, but not in general. As discussed in Section~\ref{sec:flat-syntax},
when this is the case, we are able to prove certain properties of the calculus.

@@

The call-by-value evaluation strategy holds for a wide range of flat coeffect calculi, including all
our three examples. However, it is rather weak -- in order to use it, the concrete semantics needs
to provide a way for reducing context-dependent term $\coctx{\Gamma}{\cclrd{r}} \vdash e : \tau$ to
a term $\coctx{\Gamma}{\cunit} \vdash e' : \tau$ with no context requirements.

@@

\begin{lemma}[Bottom-pointed substitution]
\label{thm:cbn-substitution-bot}
In a bottom-pointed flat coeffect calculus with an algebra $(\C, \cseq, \cpar, \czip, \cunit, \czero, \cleq)$ 
where $\czip = \cseq = \cpar$ and the operation is also idempotent and commutative and
$\cclrd{r}\,\cleq\,\cclrd{r'} \Rightarrow \forall\cclrd{s}.\cclrd{r}\,\cseq\,\cclrd{s}\;\cleq\;\cclrd{r'}\,\cseq\,\cclrd{s}$ then:
%
\begin{equation*}
\begin{array}{l}
\coctx{\Gamma}{\cclrd{s}} \vdash e_s : \tau_s \;\; \wedge \;\; 
\coctx{\Gamma_1,  x : \tau_s, \Gamma_2}{ \cclrd{r}  } \vdash e_r : \tau_r\\
\quad \Rightarrow \;\; \coctx{\Gamma_1,\Gamma,\Gamma_2}{ \cclrd{r} \,\cseq\, \cclrd{s} } \vdash \subst{e_r}{x}{e_s} : \tau_r
\end{array}
\end{equation*}

\end{lemma}
\begin{proof}
By induction over $\vdash$, using the idempotent, commutative monoid structure to keep $\cclrd{s}$ with
the free-variable context. See Appendix~\ref{sec:appendix-flat-cbn}.
\end{proof}
